\documentclass[12pt,a4paper,titlepage]{memoir}
\usepackage[]{ruthesis}
%% Options in []:
%% IS Icelandic is main language
\title{Ph.D.\ Dissertation Template for \theInstitution{}}{Ph.D.\ Dissertation Template for \theInstitution{} in Icelandic}
\author{Joseph T. Foley}%Use \and as an author separator
\date{2020}{2}{2}%{Year}{Month}{Day}%use numbers

%\DocumentInfo{TYPE}{ABBREVIATION}{DEGREE}{PROGRAM}
%\DocumentInfo{Dissertation}{Ph.D.}{Doctor of Philosophy}{Computer Science}
\DocumentInfo{Dissertation}{Ph.D.}{Doctor of Philosophy}{Computer Science}
\School{School of Technology}

%% PhD only have Thesis Committee with roles.  Examiner is part of committee.
\SupervisorHeading{Thesis Committee}
\Supervisors{
  \personinfo{Superior A. Teacher}{Supervisor}{Professor}{Reykjavik University}{Iceland}
  \personinfo{Helpful A. Teacher}{Co-advisor}{Assistant Professor}{University of Iceland}{Iceland}
  \personinfo{Tough E. Questions}{Examiner}{Associate Professor}{Massachusetts Institute of Technology}{USA}
}

%%%%%%%%%%%%%% INDEX SETUP %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% The Memoir package (which we use) automatically generates the index
%% See section 17.2 on page 302 of the guide
%% http://texdoc.net/texmf-dist/doc/latex/memoir/memman.pdf
%% This means you have to run "makeindex DEGREE-NAME-YEAR"
\makeindex{}
\indexintoc{}

%%%%%% Useful Packages %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{lipsum}%provides us with text for testing
%% usage: \lipsum[STARTNUM-ENDNUM]

\usepackage{siunitx}
%%% Macros for SI Units in text
%% e.g. \SI{9.8}{\meter\per\second}

\usepackage[final]{listings}
%%% Formatting code inclusion and snippets
%% "final" option to force it to display code

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\maketitle
\copyrightpage{}
\signaturepage{}
\archivesigpage{}

\begin{abstract}
  The abstract goes here translated into English.
  If the thesis is in English, it should come first.
  It should be a fairly short summary of the entire document.
\end{abstract}

\begin{abstractIS}
  The abstract goes here translated into Icelandic.
  If the thesis is in Icelandic, it should come first.
  It should be a fairly short summary of the entire document.
\end{abstractIS}

\begin{dedications}
  I dedicate this to my spouse/child/pet/power animal.
\end{dedications}

\enableindents{}% turn on/off paragraph indents
% RUM: "Acknowledgements (optional)"%start numbering

\chapter*{Acknowledgements} 
\begin{quotation}
So long, and thanks for all the fish.
\end{quotation}\sourceatright{Douglas Adams\cite{adams84fish}}
\vspace{\baselineskip}

This work was funded by \the\year~RANNIS grant ``Survey of man-eating Minke whales'' 1415550.
Additional equipment was generously donated by the Icelandic Tourism Board.

{\em Acknowledgements are optional; comment this chapter out if they are absent
  Note that it is important to acknowledge any funding that helped in the work}



\chapter*{Preface}
% RUM: "Preface (optional)"
This dissertation is original work by the author, Firstname~Lastname.
Portions of the introductory text are used with permission from
Student et al.\cite{student2015awesome} of which I am an author.

  
{\em The preface is an optional element
  explaining a little who performed what work.  See
  \url{https://www.grad.ubc.ca/sites/default/files/materials/thesis_sample_prefaces.pdf}
  for suggestions.
  
  List of publications as part of the preface is
  optional unless elements of the work have already been published.
  It should be a comprehensive list of all publications in which
  material in the thesis has appeared, preferably with references to
  sections as appropriate.  This is also a good place to state
  contribution of student and contribution of others to the work
  represented in the thesis.
}


%\chapter*{Publications}
%% Some Dissertations present the related papers first, but this is sometimes in Preface
\clearpage{}
\tableofcontents{}\clearpage
\listoffigures{}\clearpage
\listoftables{}\clearpage

%% The list of abbreviations is an example of a special list
%% Other lists may be added, such as lists of algorithms, symbols, theorems, etc.
%% IN CS PhD, this is sometimes centered.
\chapter*{List of Abbreviations}%%RUM: Not mentioned
\begin{tabular}{ll}
MSc &Masters of Science\\
PhD &Doctor of Philosophy\\
\end{tabular}

\chapter*{List of Symbols}%%RUM: Not mentioned
\begin{tabular}{lll}
Symbol &Description &Value/Units\\
$E$ &Energy &\si{\joule}\\
$m$ &Mass &\si{gram}\\
$c$ &Speed of Light &\SI{2.99E8}{\meter\per\second\square}\\
\end{tabular}


\mainmatter{}
\aliaspagestyle{chapter}{empty}
% Don't put page numbers on the chapter changes

%% If you would like to separate chapters into different files, use
%% \include{chapterfile}
%% WARNING: Make sure that all of these files (and any new ones)
%% are UTF-8 otherwise you will get weird encoding errors.
\part{The First Part} % Parts optional but useful in longer documents
\chapter{The First Chapter}
\include{introduction}%Chapter in introduction.tex
\section{Another Section}
\part{The Second Part} % Parts optional but useful in longer documents

\bibliographystyle{ieeetran}
\bibliography{references}

%% If appendices are needed, uncomment the following line
%% and include the appendices in separate files
\appendix{}%%RUM: "Appendicies (as appropriate)
\input{code} % as an example, perhaps some of your code

%\backmatter{} % Sections after this don't get numbers
%% We prefer that all elements be numbered

%%%%%%%%%%%%% SHOW INDEX %%%%%%%%%%%%%%%%%%
%% Index, optional.  A good idea on longer documents
\clearforchapter{}
\printindex{}%%RUM: Not mentioned

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "PHD-NAME-YEAR"
%%% End:
